---
title: "Offensive Contribution Prediction Model of Players Based on La Liga 2023/2024 Season"
author: "Jingwei Chen"
format: 
  closeread-html:
    theme: cosmo
    cr-section:
      layout: sidebar-left
    cr-style:
      section-background-color: white
      narrative-background-color-sidebar: lightblue
      narrative-text-color-sidebar: black
      narrative-font-size: 1em
      narrative-sidebar-width: 300px
embed-resources: true
---

```{r setup, include=FALSE}
# load packages and/or import data set(s)
library(tidyverse)
library(plotly)
soccer <- read_csv("S2324-laliga-players.csv")
```

:::: {.cr-section}

Categorizing or changing our data. @cr-code1

::: {#cr-code1}
According to our orinigal csv document, we would like to combine the data of "shots_off_target_inc_woodwork" 

and "shots_on_target_inc_goals" together to form a new variable "shots".
```{r}
#| echo: true
soccer <- soccer |>
    mutate(shots = shots_off_target_inc_woodwork + shots_on_target_inc_goals)
```

We also have to filter out those players who have no goals thorought the season, because factors like 

injury and special position (GK specifically) will have a dramatic impact to our goal prediction model.
```{r}
#| echo: true
soccer <- soccer |>
    filter(goals > 0)
```
:::

::::

:::: {.cr-section}

Now, we take a look at the graph. @cr-plot1

::: {#cr-plot1}
```{r}
#| warning: false
#| message: false

plot <- soccer |>
  ggplot(aes(x = total_passes, y = goals, color = position)) +
  geom_point(size = 0.8) +
  geom_smooth(method = "lm") +
  labs(
    x = "Total Passes",
    y = "Goals",
    title = "Scatter Plot of Each Goal Scorers' Data of Goals and Passes"
  )

plot
```
:::

::::

:::: {.cr-section}

Some elements inside the regression line. @cr-text1

::: {#cr-text1}
To form a regression line, we have to consider what are some important factors that would potentially contribute to a goal:

· Total Passes

· Successful Dribbles

· Corners Won

· Penalties Taken

· Shots

```{r}
#| echo: true
model <- lm(goals ~ total_passes + successful_dribbles + corners_won + penalties_taken + shots, data = soccer)
model
```
:::

Let's predict by randomly choosing a player from La Liga. @cr-text2

::: {#cr-text2}

Given that, in La Liga 2023/2024 season, the player Artem Dovbyk has a data of 386 total passes, 17 successful dribbles, 

12 corners won, 8 penalties taken, and 77 shots, we can predict his total season goal by importing these data into our 

goal prediction model.

```{r}
#| echo: true
data <- data.frame(total_passes = 386,
                   successful_dribbles = 17,
                   corners_won = 12,
                   penalties_taken = 8,
                   shots = 77)
```
:::

Checking our goal prediction number with the real goal number. @cr-text3

::: {#cr-text3}
```{r}
#| echo: true
predict(model, data)
```

So, the predicted goals is `r predict(model, data)`, which is approximately 22 goals, and let's reveal the Artem Dovbyk's real goals:

```{r}
#| echo: true
soccer$goals[soccer$name == "Artem Dovbyk"][1]
```

We have a residual of only 2 goals; this indicates that the selected offensive variables capture a substantial portion of the player's scoring performance.
:::

Multiple Regression Line Expression. @cr-text4

::: {#cr-text4}
Expected Goals = - 0.860570 - 0.001295 * Total Passes + 0.008045 * Successful Dribbles - 0.078516 * Corners Won + 1.025462 * Penalties Taken + 0.205220 * Shots
:::

::::